### 2017-01-23 conc.tex
experiments sir corrections done

\chapter{Conclusions and Future work}\label{conc}
\label{sec:conclusions}
We presented an improved Hessian estimation scheme for the 2RDSA algorithm \cite{prashanth2015rdsa}. The proposed scheme was shown to be provably convergent to the true Hessian. We proposed generalisation of RDSA algorithm proposed in \cite{prashanth2015rdsa}. As a result of generalisation we are able to use much larger class of distributions  for perturbation random variables. The proposed generalisation inherits all the improved Hessian estimation  schemes proposed earlier. We also presented an improved Hessian estimation scheme for 2SPSA-3 algorithm \cite{bhatnagar2015simultaneous} and as a special case, for a quadratic objective resulted in a  convergence rate that is on par with the corresponding rate for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. The advantage with 2RDSA-IH, 2SPSA-3-IH is that it requires only 75\% of the simulation cost per-iteration for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. Numerical experiments demonstrated that 2RDSA-IH, 2SPSA-3-IH outperforms both 2SPSA-IH and 2SPSA without the improved Hessian estimation scheme. They also indicate that schemes with improved Hessian estimation outperforms their respective regular schemes without the improved Hessian estimation scheme. 2RDSA-IH with asymmetric Bernoulli distribution performing the best overall.

As future work, it would be interesting to derive finite time bounds that show a lower Hessian estimation error for 2RDSA-IH when compared to 2RDSA and 2SPSA. Stochastic Newton methods  methods converge faster and  are often more accurate than simple gradient search schemes. However they are computationally much costlier than first-order methods. Since first-order methods exhibits slower convergence rate and heavily depended on the step-size selection one has to resort to second-order methods. As a future work, it would be interesting to look at the methods like momentum descent, conjugate gradient methods, Hessian free optimization schemes which result in faster convergence for the first-order methods in deterministic optimization case. It would be interesting to extend those methods to stochastic optimization case and prove that they exhibits  faster convergence than first-oder methods. From application point of view it would be interesting to apply these methods to some interesting real world applications.

>>>>

\chapter{Conclusions and Future work}\label{conc}
\label{sec:conclusions}
In this thesis, we presented an improved Hessian estimation scheme for the 2RDSA algorithm \cite{prashanth2015rdsa}. The proposed scheme was shown to be provably convergent to the true Hessian. We proposed generalisations of the RDSA algorithm proposed in \cite{prashanth2015rdsa}. As a result of the generalisation, we are able to use a much larger class of distributions  for the perturbation random variables. The proposed generalisation inherits all the improved Hessian estimation  schemes proposed earlier. We also presented an improved Hessian estimation scheme for the 2SPSA-3 algorithm \cite{bhatnagar2015simultaneous} and for the special case of a quadratic objective, it resulted in a  convergence rate that is on par with the corresponding rate for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. The advantage with 2RDSA-IH, 2SPSA-3-IH is that these schemes it require only 75\% of the simulation cost per-iteration for 2SPSA with Hessian estimation improvements (2SPSA-IH) \cite{spall-jacobian}. Numerical experiments demonstrated that 2RDSA-IH, 2SPSA-3-IH outperform both 2SPSA-IH and 2SPSA without the improved Hessian estimation procesdure. They also indicate that schemes with improved Hessian estimation outperform the respective regular schemes without the improved Hessian estimation procedure. 2RDSA-IH with asymmetric Bernoulli distribution is seen to perform the best overall.

As future work, it would be interesting to look into the following directions:
\begin{enumerate}
\item Derive finite time bounds that show a lower Hessian estimation error for 2RDSA-IH when compared to 2RDSA and 2SPSA. 
\item Stochastic Newton methods converge faster and  are often more accurate than simple gradient search schemes. However they are computationally much costlier than first-order methods. Since first-order methods exhibit slower convergence rate and heavily depend on the step-size selection one has to resort to second-order methods for improved performance. As a future work, it would be interesting to look at  methods such as momentum descent, conjugate gradient as well as, Hessian free optimization approaches which result in faster convergence for the first-order methods and are known to be computationally cheaper than second-order methods in the deterministic optimization scenario. It would be interesting to extend those methods to the stochastic optimization setting and prove that they exhibit  faster convergence than first-order methods and result in lower computational cost. 
\item In the methods described in this thesis the perturbations used are random variables. In \cite{bhatnagar2003two}, for the first-order SPSA method,  construction of two different deterministic  perturbation schemes was proposed and  under certain conditions on the perturbation vectors and noise sequences, the algorithm is shown to converge. The idea behind using deterministic perturbations is to reduce the bias in the gradient estimates. It would be interesting to extend this construction to the RDSA scheme as well. And moreover this kind of construction for second-order methods is not available for both SPSA and RDSA. One can use the above ideas and show significant improvements to the existing methods.
\item From an application point of view it would be interesting to apply these methods to some interesting real world applications. It would be interesting to explore applications of  these methods  to the design of reinforcement learning algorithms.
\end{enumerate}

### 2017-01-23 experiments.tex
experiments sir corrections done

\paragraph{Fourth-order loss}
\begin{align} 
f(x) = \theta\tr A\tr A \theta + 0.1 \sum_{j=1}^N (A\theta)^3_j + 0.01 \sum_{j=1}^N (A\theta)^4_j.\label{eq:4thorder}
 \end{align} 
The optimum $\theta^*$ for above $f$ is $\theta^*=0$, with $f(\theta^*) = 0$.

@@

\begin{table}
\centering
 \caption{Normalized loss values for fourth-order  objective \eqref{eq:4thorder} with and without noise: standard error from $500$ replications shown after $\pm$}
\label{tab:norloss-4thf}
\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.132 \pm 0.0267$ & $0.104 \pm 0.0355$\\
&&\\
\textbf{2SPSA-3} & $0.0893 \pm 0.001$ & $0.0457 \pm 0.0004$\\
&&\\
\textbf{2RDSA-Unif} &$0.115 \pm 0.0214$ & $0.0271 \pm 0.0538$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0471 \pm 0.021$& $\bm{0.0099 \pm 0.0014}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.0795 \pm 0.0234$ & $0.0628 \pm 0.0234$\\
&&\\
\textbf{2SPSA-3} & $0.0338 \pm 0.0001$ & $0.0315 \pm 0.0007$\\
&&\\
\textbf{2RDSA-Unif} &$0.0813 \pm 0.0275$ & $0.0214 \pm 0.00376$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0199 \pm 0.0114$& $\bm{0.0098 \pm 0.00147}$\\
 \bottomrule
\end{tabular}
}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%% Quadratic
\begin{table}
\centering
 \caption{Normalized loss values for quadratic objective \eqref{eq:quadratic} with and without noise: standard error from $500$ replications shown after $\pm$}
\label{tab:norloss-quadratic}
\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $-0.0062 \pm 0.1164$ & $-0.1229 \pm 0.1374$\\
&&\\
\textbf{2SPSA-3} & $-0.0161 \pm 0.0955$ & $-0.2748 \pm 0.0629$\\
&&\\
\textbf{2RDSA-Unif} &$0.0485 \pm 0.1465$ & $-0.259 \pm 0.0398$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $-0.2564 \pm 0.068$& $\bm{-0.2877 \pm 0.0051}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $-0.0785 \pm 0.1178$ & $-0.1716 \pm 0.1339$\\
&&\\
\textbf{2SPSA-3} & $-0.0667 \pm 0.0602$ & $-0.2793 \pm 0.0625$\\
&&\\
\textbf{2RDSA-Unif} &$0.0326 \pm 0.1599$ & $-0.2672 \pm 0.0299$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $-0.2777 \pm 0.0488$& $\bm{-0.2881 \pm 0.0012}$\\
 \bottomrule
\end{tabular}}

@@

%%%%%%%%%%%%%% NMSE for quadratic
\begin{table}
\centering
 \caption{NMSE values for quadratic objective \eqref{eq:quadratic} with and without noise: standard error from $500$ replications shown after $\pm$}
\label{tab:nmse-quadratic}
%\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.9491 \pm 0.0131$ & $0.5495 \pm 0.0217$\\
&&\\
\textbf{2SPSA-3} & $0.8378 \pm 0.0179$ & $0.1045 \pm 0.0005$\\
&&\\
\textbf{2RDSA-Unif} &$1.0073 \pm 0.0140$ & $0.1953 \pm 0.0095$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.1667 \pm 0.0095$& $\bm{0.0324 \pm 0.0007}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.7325 \pm 0.0180$ & $0.3939 \pm 0.0230$\\
&&\\
\textbf{2SPSA-3} & $0.6661 \pm 0.01554$ & $0.0684 \pm 0.0006$\\
&&\\
\textbf{2RDSA-Unif} &$0.9834 \pm 0.0170$ & $0.1623 \pm 0.0086$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0686 \pm 0.0078$& $\bm{0.0316 \pm 0.0006}$\\
 \bottomrule
\end{tabular}
\end{table}

Tables \ref{tab:norloss-4thf}--\ref{tab:norloss-quadratic} present the normalized loss values observed for the four algorithms - 2SPSA, 2SPSA-3, 2RDSA-Unif and 2RDSA-AsymBer - with/without improved Hessian estimation scheme and for the fourth-order and quadratic loss functions, respectively. Table \ref{tab:nmse-quadratic} presents the NMSE values obtained for the aforementioned algorithms with the quadratic loss. The results in Tables \ref{tab:norloss-4thf}--\ref{tab:nmse-quadratic} are obtained after running all the algorithms with a budget of $10000$ function evaluations.

 Figures \ref{fig:norlossvssims}, \ref{fig:norlossvssimsspsa-3} plots the normalized loss as a function of the simulation budget with the fourth-order loss objective with $\sigma=0.1$ for algorithms 2RDSA and 2SPSA-3 respectively when compared with 2SPSA. Figures \ref{fig:QuadnorlossvssimsNoiseless}, \ref{fig:QuadnorlossvssimsNoiselessspsa3} plots the normalized loss as a function of the simulation budget with the quadratic loss objective with $\sigma=0$ for algorithms 2RDSA and 2SPSA-3 respectively when compared with 2SPSA. See Figures \ref{fig:norlossvssimsNoiseless}-- \ref{fig:QuadnorlossvssimsNoisy} and \ref{fig:norlossvssimsNoiselessspsa3}-- \ref{fig:QuadnorlossvssimsNoisyspsa3} for similar results with $\sigma = 0$ for fourth-order loss and $\sigma=0.1$ for quadratic loss. 
 From the results in Tables \ref{tab:norloss-4thf}--\ref{tab:nmse-quadratic} and Figures, we make the following observations:

 \textit{\textbf{Observation 1:} Schemes with improved Hessian estimation performs better than their respective regular schemes.}

@@

\textit{\textbf{Observation 4:} 2RDSA-IH-AsymBer performing the best overall.}

>>>>

\paragraph{Fourth-order loss}
\begin{align} 
f(x) = \theta\tr A\tr A \theta + 0.1 \sum_{j=1}^N (A\theta)^3_j + 0.01 \sum_{j=1}^N (A\theta)^4_j.\label{eq:4thorder}
 \end{align} 
The optimum $\theta^*$ for the above $f$ is $\theta^*=0$, with $f(\theta^*) = 0$.

@@

\begin{table}
\centering
 \caption{Normalized loss values for fourth-order  objective \eqref{eq:4thorder} with and without noise: standard error from $500$ is replications shown after $\pm$.}
\label{tab:norloss-4thf}
\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.132 \pm 0.0267$ & $0.104 \pm 0.0355$\\
&&\\
\textbf{2SPSA-3} & $0.0893 \pm 0.001$ & $0.0457 \pm 0.0004$\\
&&\\
\textbf{2RDSA-Unif} &$0.115 \pm 0.0214$ & $0.0271 \pm 0.0538$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0471 \pm 0.021$& $\bm{0.0099 \pm 0.0014}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.0795 \pm 0.0234$ & $0.0628 \pm 0.0234$\\
&&\\
\textbf{2SPSA-3} & $0.0338 \pm 0.0001$ & $0.0315 \pm 0.0007$\\
&&\\
\textbf{2RDSA-Unif} &$0.0813 \pm 0.0275$ & $0.0214 \pm 0.00376$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0199 \pm 0.0114$& $\bm{0.0098 \pm 0.00147}$\\
 \bottomrule
\end{tabular}
}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%% Quadratic
\begin{table}
\centering
 \caption{Normalized loss values for quadratic objective \eqref{eq:quadratic} with and without noise: standard error from $500$ replications is shown after $\pm$.}
\label{tab:norloss-quadratic}
\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $-0.0062 \pm 0.1164$ & $-0.1229 \pm 0.1374$\\
&&\\
\textbf{2SPSA-3} & $-0.0161 \pm 0.0955$ & $-0.2748 \pm 0.0629$\\
&&\\
\textbf{2RDSA-Unif} &$0.0485 \pm 0.1465$ & $-0.259 \pm 0.0398$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $-0.2564 \pm 0.068$& $\bm{-0.2877 \pm 0.0051}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $-0.0785 \pm 0.1178$ & $-0.1716 \pm 0.1339$\\
&&\\
\textbf{2SPSA-3} & $-0.0667 \pm 0.0602$ & $-0.2793 \pm 0.0625$\\
&&\\
\textbf{2RDSA-Unif} &$0.0326 \pm 0.1599$ & $-0.2672 \pm 0.0299$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $-0.2777 \pm 0.0488$& $\bm{-0.2881 \pm 0.0012}$\\
 \bottomrule
\end{tabular}}

@@

%%%%%%%%%%%%%% NMSE for quadratic
\begin{table}
\centering
 \caption{NMSE values for quadratic objective \eqref{eq:quadratic} with and without noise: standard error from $500$ replications is shown after $\pm$.}
\label{tab:nmse-quadratic}
%\scalebox{0.8}{
\begin{tabular}{|c|c|c|}
\toprule
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0.1$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.9491 \pm 0.0131$ & $0.5495 \pm 0.0217$\\
&&\\
\textbf{2SPSA-3} & $0.8378 \pm 0.0179$ & $0.1045 \pm 0.0005$\\
&&\\
\textbf{2RDSA-Unif} &$1.0073 \pm 0.0140$ & $0.1953 \pm 0.0095$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.1667 \pm 0.0095$& $\bm{0.0324 \pm 0.0007}$\\
 \bottomrule
 %%%%%%%%%%%%2nd ordr
\rowcolor{gray!20}
\multicolumn{3}{||c|}{\multirow{2}{*}{\textbf{Noise parameter $\sigma=0$}}}\\[1em]
%&&&\\
\midrule
  & \multirow{2}{*}{\textbf{Regular}} & \textbf{Improved Hessian}  \\
  & & \textbf{ estimation} \\
 \midrule
\textbf{2SPSA} & $0.7325 \pm 0.0180$ & $0.3939 \pm 0.0230$\\
&&\\
\textbf{2SPSA-3} & $0.6661 \pm 0.01554$ & $0.0684 \pm 0.0006$\\
&&\\
\textbf{2RDSA-Unif} &$0.9834 \pm 0.0170$ & $0.1623 \pm 0.0086$\\ 
&&\\
\textbf{2RDSA-AsymBer}& $0.0686 \pm 0.0078$& $\bm{0.0316 \pm 0.0006}$\\
 \bottomrule
\end{tabular}
\end{table}

Tables \ref{tab:norloss-4thf}--\ref{tab:norloss-quadratic} present the normalized loss values observed for the four algorithms - 2SPSA, 2SPSA-3, 2RDSA-Unif and 2RDSA-AsymBer - with/without improved Hessian estimation scheme and for the fourth-order and quadratic loss functions, respectively. Table \ref{tab:nmse-quadratic} presents the NMSE values obtained for the aforementioned algorithms with the quadratic loss. The results in Tables \ref{tab:norloss-4thf}--\ref{tab:nmse-quadratic} are obtained after running all the algorithms with a budget of $10,000$ function evaluations.

 Figures \ref{fig:norlossvssims}, \ref{fig:norlossvssimsspsa-3} plot the normalized loss as a function of the simulation budget with the fourth-order loss objective with $\sigma=0.1$ for algorithms 2RDSA and 2SPSA-3 respectively when compared with 2SPSA. Figures \ref{fig:QuadnorlossvssimsNoiseless}, \ref{fig:QuadnorlossvssimsNoiselessspsa3} plot the normalized loss as a function of the simulation budget with the quadratic loss objective with $\sigma=0$ for algorithms 2RDSA and 2SPSA-3 respectively when compared with 2SPSA. See Figures \ref{fig:norlossvssimsNoiseless}-- \ref{fig:QuadnorlossvssimsNoisy} and \ref{fig:norlossvssimsNoiselessspsa3}-- \ref{fig:QuadnorlossvssimsNoisyspsa3} for similar results with $\sigma = 0$ for fourth-order loss and $\sigma=0.1$ for quadratic loss. 
 From the results in Tables \ref{tab:norloss-4thf}--\ref{tab:nmse-quadratic} and Figures, we make the following observations:

 \textit{\textbf{Observation 1:} Schemes with improved Hessian estimation perform better than their respective regular schemes.}

@@

\textit{\textbf{Observation 4:} 2RDSA-IH-AsymBer perform the best overall.}

### 2017-01-23 second-order-spsa-3.tex
experiments sir corrections done

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n &=    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    \nabla^2 f(\theta^*) +\Psi_{n}(\nabla^2 f(\theta^*))\nonumber\\
 &=    H^* +\Psi_{n}(H^* ),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*)).
\end{align}
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}. The above stochastic approximation algorithm aimed at finding the roots of the equation $H-H^*=0$. In \eqref{eq:hhatexpanded}, $\E (\widehat \Psi_n - \Psi_n (H^*) | \F_n) = 0 \,\,\ a.s$.  Given a Lyapunov function, one can  the conditions required to show  the mean square convergence of the \eqref{eq:hhatexpanded} from the \cite{nevel1973stochastic}, pp.92-94. It is easy to see that $V(H) = \frac{1}{2} (H-H^*)\tr(H-H^*)$ indeed serves as Lyapunov function. From part (i) in Theorem 3 of \cite{spall-jacobian}, one can check that our algorithm indeed satisfy those conditions,  which in turn implies the $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0 \,\,\,a.s.$ as $n\rightarrow \infty$.

>>>>

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n &=    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    \nabla^2 f(\theta^*) +\Psi_{n}(\nabla^2 f(\theta^*))\nonumber\\
 &=    H^* +\Psi_{n}(H^* ),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
%This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*)).
\end{align}
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}. The above stochastic approximation algorithm aimed at finding the roots of the equation $H-H^*=0$. In \eqref{eq:hhatexpanded}, $\E (\widehat \Psi_n - \Psi_n (H^*) | \F_n) = 0 \,\,\ a.s$.  Given a Lyapunov function, one can  get the conditions required to show  the mean square convergence of the \eqref{eq:hhatexpanded} from the \cite{nevel1973stochastic}, pp.92-94. It is easy to see that $V(H) = \frac{1}{2} (H-H^*)\tr(H-H^*)$ indeed serves as Lyapunov function. From part (i) in Theorem 3 of \cite{spall-jacobian}, one can check that our algorithm indeed satisfy those conditions,  which in turn implies the $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0 \,\,\,a.s.$ as $n\rightarrow \infty$.
